Refinement for open automata

### 2021-05-06 2021-Refinement/report.tex
Added meeting TODOS

To illustrate these definitions we consider  two implementations (figure \ref{fig:enable}) of the LOTOS\marginpar{cite something here} operator enable in the open automata model.
The enable operator runs  the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}.

@@

\begin{figure}
\centering
\input{Traffic_Lights_Spec.tex}
\caption{The specification of a traffic light system}
\label{fig:tls}
\end{figure}
\begin{figure}
\centering
\input{Traffic_Lights_Controller.tex}
\vrule
\input{Traffic_Lights_Register.tex}
\caption{On the left: The controller agent; On the right: The counter agent}
\label{fig:tlh}
\end{figure}
The component we choose to compose in the holes are in Figure \ref{fig:tlh}.
On the left is the controller agent which will be composed in the hole \(C\).
Its role is to decide the duration before switching the lights.
This implementation is simply a constant time for each color.

@@

The automaton on Figure \ref{fig:tlf} is bisimilar to the composition of the specification on Figure \ref{fig:tls} and the agents on Figure \ref{fig:tlh}.
The result of the composition has 36 states (\(3 \times 2 \times 6\)) but only 6 are reachable from the initial configuration.
The transitions obtained by composition are the following (generic and simplified version). \Ludo{Also satisfiable guards were replaced with simplified equivalent}{moved but a rephrasing may be better: simplified twice?}:

\Ludo{TODO: exlpain X}{}

@@

In the state \(RC\) the composition makes 2 transition \Ludo{from}{be more precise} the \(\tau\) transition but both have a false guard; \Ludo{Let's look}{avoid informal english} at one of them.
\nmm{\OT{RC}{\mpar{R, 3, C}}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
Obviously the guard is false so  it is equivalent to have no transition.
\Ludo{rest of the paragraph}{why so much discussion on a useless transition? did I miss something?} Also the guard  can be simplified.
In this article the guard and transition are always simplified except for the sake of illustrating a concept that is lost in the simplification as it is the case here.
We can see that the \(x\) variables from the specification, the controller and the register are in conflict.
To resolve the conflict we renamed the variables.

In the state \(RS\) the composition makes 1 transition from the \(\tau\) transition.
This transition is described before but \Ludo{Let's look}{avoid informal english} at the details of the composition.
The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained new values of the variables is \(\mbrc{t \gets x_R, c \gets 0}\).
We can see here how value passing works: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the register.
This guard and \Ludo{value update}{what do you mean?} can be simplified to the one shown on the drawing.
Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is fixed before the transition and its value cannot be set outside of the variable update, hence the use of a local variable \(x\).
\end{exi}

>>>>

To illustrate these definitions we consider  two implementations (figure \ref{fig:enable}) of the LOTOS \cite{ISOLOTOS} operator enable in the open automata model.
The enable operator runs  the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}.

@@

\begin{figure} % TODO: consistency on register and counter, make number appear in the full composed, Change C so that is it not both a state and a hole
\centering
\input{Traffic_Lights_Spec.tex}
\caption{The specification of a traffic light system}
\label{fig:tls}
\end{figure}
\begin{figure}
\centering
\input{Traffic_Lights_Controller.tex}
\vrule
\input{Traffic_Lights_Register.tex}
\caption{On the left: The controller agent; On the right: The counter agent}
\label{fig:tlh}
\end{figure}
The component we choose to compose in the holes are in Figure \ref{fig:tlh}.
On the left is the controller agent which will be composed in the hole \(C\).
Its role is to decide the duration before switching the lights.
This implementation is simply a constant time for each color.

@@

The automaton on Figure \ref{fig:tlf} is bisimilar to the composition of the specification on Figure \ref{fig:tls} and the agents on Figure \ref{fig:tlh}.
The result of the composition has 36 states (\(3 \times 2 \times 6\)) but only 6 are reachable from the initial configuration.
The transitions obtained by composition are the following (generic and simplified version). \Ludo{Also satisfiable guards were replaced with simplified equivalent}{moved but a rephrasing may be better: simplified twice?}:
% TODO: explain what you simplified

\Ludo{TODO: exlpain X}{} % TODO: generic = XXX stands for Red Green or Yellow

@@

In the state \(RC\) the composition makes 2 transition \Ludo{from}{be more precise} the \(\tau\) transition but both have a false guard; \Ludo{Let's look}{avoid informal english} at one of them. % TODO: Insist on the fact that it shows many usefull states and mechanisms and why it is useless
\nmm{\OT{RC}{\mpar{R, 3, C}}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
Obviously the guard is false so  it is equivalent to have no transition.
\Ludo{rest of the paragraph}{why so much discussion on a useless transition? did I miss something?} Also the guard  can be simplified.
In this article the guard and transition are always simplified except for the sake of illustrating a concept that is lost in the simplification as it is the case here.
We can see that the \(x\) variables from the specification, the controller and the register are in conflict.
To resolve the conflict we renamed the variables.

In the state \(RS\) the composition makes 1 transition from the \(\tau\) transition.
This transition is described before but \Ludo{Let's look}{avoid informal english} at the details of the composition.
The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained new values of the variables is \(\mbrc{t \gets x_R, c \gets 0}\).
We can see here how value passing works: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the register.
This guard and \Ludo{value update}{what do you mean?} can be simplified to the one shown on the drawing. % TODO: Variable assignment
Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is fixed before the transition and its value cannot be set outside of the variable update, hence the use of a local variable \(x\).
\end{exi}
